\cvsection{Co-Curricular}

\begin{itemize}
\item \textbf{Founded University’s Open Source Club} with the aim of creating more awareness and getting more upstream contributors.
\item \textbf{Mentor, Google Code-In} 2017 \& 2018.
Responsible for triaging issues, reviewing Pull Requests. Established \textit{contributing guidelines} for Vulture.
\item \textbf{Mentor, Kharagpur Winter of Code 2017}
\item Open Source Contributions to \href{https://github.com/python/cpython/commits/master?author=RJ722}{\underline{CPython}.}
\end{itemize}

\cvsection{Speaking Experience}
\cvachievement{\faMicrophone}{PyCon India 2017}{``\textit{Reducing Dead Code Ratio of Python Programs}" + Lightning Talk about Code Linting}

\cvachievement{\faMicrophone}{DevConf India [2018]; Czech [2019]}{Talk: ``\textit{Using Vulture to improve used to unused ratio of Python Programs.}"}

\cvachievement{\faMicrophone}{Autonomous Underwater Vehicle Workshop}{Spoke about ``\textit{Challenges in building an Underwater Vehicle}"}

\cvsection{Skills \& Tools}

\cvtag{Python} 
\cvtag{C++}
\cvtag{JavaScript}
\cvtag{MATLAB}

\divider\smallskip

\cvtag{Flask}
\cvtag{ROS}
\cvtag{rviz}
\cvtag{OpenCV}
\cvtag{Pandas}
\cvtag{FastAI}
\cvtag{PyTorch}
\cvtag{CARLA}

\divider\smallskip

\cvtag{Git}
\cvtag{\LaTeX}
\cvtag{Emacs}
\cvtag{Jupyter}
\cvtag{zsh}
% \cvtag{Embedded Systems}
% \cvtag{Statistical Analysis}

% \cvsection{Languages}
% 
% \cvskill{English}{5}
% \divider
% 
% \cvskill{Spanish}{4}
% \divider
% 
% \cvskill{German}{3}

%% Yeah I didn't spend too much time making all the 
%% spacing consistent... sorry. Use \smallskip, \medskip, 
%% \bigskip, \vpsace etc to make ajustments.
\medskip

\cvsection{Education}

\cvevent{B.Tech. (Electronics Engineering)}{Aligarh Muslim University}{Aug. 2016 -- May 2020}{}

CPI: 8.5 / 10.0

\cvsection{Referees}

% \cvref{name}{email}
\cvref{Prof. Ekram Khan}{ekhan.el@amu.ac.in}
\divider
\cvref{Dr. Jendrik Seipp}{jendrik.seipp@unibas.ch}
\divider